---
title: "Decision analysis methods guide"
author:
- Eike Luedeling$^1$
- Cory Whitney$^1$
- $^1$University of Bonn, Germany
csl: academy-of-management-review.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: preamble-latex.tex
      latex_engine: xelatex
    number_sections: yes
subtitle: Agricultural policy for nutrition
bibliography: bib/Methods_Refs.bib
---


<!-- add    toc: yes to YAML for Table of Contents
add 
devtools::install_github("rstudio/bookdown") 
To run LaTeX
devtools::install_github('yihui/tinytex')
tinytex::install_tinytex()
--> 

<!-- Suggest we target Rural 21 with this manuscript http://www.rural21.com/home/ --> 

\tableofcontents
\listoffigures
\listoftables 

**List of abbreviations**

\begin{itemize}
  \item Applied Information Economics (AIE)
  \item Conditional Probability Tables (CPTs)
  \item Confidence Interval (CI)
  \item Expected Monetary Value (EMV)
  \item Expected Value or perfect information (EVPI)
  \item Node Probability Table (NPT)
  \item Value of Information (VoI)
\end{itemize}



```{r child="Summary.Rmd"}
```


```{r child="Introduction.Rmd"}
```

#Steps in the Decision Analysis process

```{r child = "Decision_framing.Rmd"}
```

```{r child="Generating_a_graphical_model.Rmd"}
```

```{r child = "Calibration_training.Rmd"}
```

```{r child = "Model_Quantification.Rmd"}
```

```{r child = "Value_of_Information_analysis.Rmd"}
```

```{r child = "The_decisionSupport_package.Rmd"}
```

```{r child = "Conclusions.rmd"}
```

```{r child="References.Rmd"}
```
